ME780 Assignment 2

### 2016-03-31 assignments/assignment_2/report.tex
Add working prm for assignment

A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line ahead of the closest point on the line to the current robot position.

>>>>

A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line, ahead of the closest point on the trajectory line to the current robot position.

\subsection{Closest Point on the Trajectory Line to the Robot}
The closest point between the robot's position and the trajectory line can be calculated, . Let $A$ and $B$ be the start and end of a trajectory line, the first step is to find the gradient $m_{1}$ of trajectory line $AB$.

\begin{align}

\end{align}

The closest point $Q$ on the trajectory line $AB$ relative to the robot at point $P$ is then:

m_{2} = -1 / m_{1};
x = (m_{1} * x_{1} - m_{2} * a + b - y_{1}) / (m_{1} - m_{2});
y = m_{2} * (x - a) + b;
